Revisiting the Austral Spring Extratropical Southern Hemisphere zonally asymmetric circulation using complex Empirical Orthogonal Functions

### 2022-05-27 analysis/paper/shceof.Rmd
Agrega aclaración de eventos ENSO

The correlation between the absolute magnitude of the ONI index and the  cEOF2 amplitude is `r cor_enso_mag$text`. 
However, this relationship is mostly driven by the three years with strongest ENSO events in the period (`r knitr::combine_words(year(gdata[order(-oni)][1:3]$time))`) which coincide with the three years with strongest cEOF2 magnitude (not shown).
If those years are removed, the correlation becomes non-significant (`r cor_enso_mag_outlier$text`).
Furthermore, even when using all years, the Spearman correlation --which is robust to outliers-- is also non-significant (`r signif(cor_enso_spearman$estimate, 2)`, p-value`r report_p(cor_enso_spearman$p.value)`). 
Therefore, although the location of tropical SST anomalies seem to have an effect in defining the phase of the cEOF2, the relationship between the magnitude of cEOF2 and ONI remains uncertain.

>>>>

The correlation between the absolute magnitude of the ONI index and the  cEOF2 amplitude is `r cor_enso_mag$text`. 
However, this relationship is mostly driven by the three years with strongest ENSO events in the period (`r knitr::combine_words(year(gdata[order(-oni)][1:3]$time))`) which coincide with the three years with strongest cEOF2 magnitude (not shown).
If those years are removed, the correlation becomes non-significant (`r cor_enso_mag_outlier$text`).
Furthermore, even when using all years, the Spearman correlation --which is robust to outliers-- is also non-significant (`r signif(cor_enso_spearman$estimate, 2)`, p-value`r report_p(cor_enso_spearman$p.value)`). 
Therefore, although the location of tropical SST anomalies seem to have an effect in defining the phase of the cEOF2, the relationship between the magnitude of cEOF2 and ONI remains uncertain might be evident only in particularly intense ENSO events, for which there are few data.
